---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
### tuckerR.mmgg

This package performs Three-Mode Principal Components using Tuckers Models and plot interactive Biplot.Some experiment design generated three-way or three-mode data, repeated observations of a set of attributes for a set of individuals in different conditions. The information was displayed in a three-dimensional array, and the structure of the data was explored using Three-Mode Principal
Component Analysis, the Tucker-2 Model. 

### Installation

```{r installation, eval = FALSE}
devtools::install_github("gusart/tuckerR_mmgg")
```
  
### Important contribution of this package
The most important contribution of this package are the interactive biplot graphics and the application of the `diffit()`  function to find the best combination of components to retain.

```{r}
library(tuckerR.mmgg)
data(maize_pop)
output <- tucker2R(maize_pop,amb=2,stand=TRUE,nc1=3,nc2=3)
```

###Extract the core matrix.

```{r}
output$matrizG  
```

###The plot from output of function

```{r}
plot(output) 
```
